---
title: "Project proposal"
author: "Team name"
output: github_document
---

```{r load-packages, message = FALSE}
library(tidyverse)
library(broom)
library(ggridges)
```

*For instructions on what each section should include, please see the [project page](https://idsed.digital/assessments/project/#proposal) on the course website. Remove this text when completing your proposal*.

## 1. Introduction

Our aim in this project is to find out how iMDb ratings compare for films from different countries. We are using a data set called iMDb movies that has come from kaggle. We will also compare how different variables (title, year published, genre, budget, USA gross income, Worldwide gross income, duration and actors) affect iMDb ratings and also how many votes were cast for a film to recieve said rating. 


## 2. Data

```{r read-data}
glimpse(imdb)
```

## 3. Data analysis plan

The outcome (response, Y) will be the average imdb ratings, The predictor (explanatory, X) will be country. To properly explore these realtionships we will use gross and worlwide income to see if the movie did well worldwide or just in the us, we can also ...

We will use comparison groups such as worldwide gross to see if this film sold well worldwide or just in the US, if it did well worldwide 

```{r data-analysis-genre}
imdb_genre <- imdb %>%
  mutate(genre = case_when(
    genre == "Sci Fi" ~ "Sci-Fi",
    TRUE ~ genre)) %>%
  separate_rows(genre)
  

imdb_genre %>%
  group_by(genre) %>%
  summarise(
    mean_rating = mean(avg_vote, na.rm = TRUE),
    median_rating = median(avg_vote, na.rm = TRUE)
    ) %>%
  arrange(desc(mean_rating))

imdb_genre %>%
  ggplot(aes(x = avg_vote, y = genre)) +
  geom_density_ridges(alpha = 0.5)
```

```{r data-analysis-income}
imdb_income <- imdb %>%
  mutate( 
  worlwide_gross_income = na_if(worlwide_gross_income, "")) %>%
  transform(worlwide_gross_income = as.numeric(gsub("\\$", "", worlwide_gross_income)))
   
imdb_income %>%
  ggplot(aes(x = worlwide_gross_income, y = avg_vote)) +
  geom_point(alpha = 0.1) +
  theme(axis.text.x = element_text(angle = 90))
```

```{r data-analysis-votes}
imdb %>%
  ggplot(aes(x = votes, y = avg_vote)) +
  geom_point(alpha = 0.1)
```

```{r data-analysis-duration}
imdb %>%
  ggplot(aes(x = duration, y = avg_vote)) +
  geom_point(alpha = 0.1)
```
```{r data-analysis-metascore}
imdb %>%
  ggplot(aes(x = metascore, y = avg_vote)) +
  geom_point(alpha = 0.2)
```