---
title: "Project proposal"
author: "Calcutta_Coders"
output: github_document
---

```{r load-packages, message = FALSE}
library(tidyverse)
library(broom)
library(ggridges)
```

## 1. Introduction

Our aim in this project is to find out how iMDb ratings compare for films from different countries. We are using a data set called iMDb movies that has come from kaggle. We will also compare how different variables (title, year published, genre, budget, USA gross income, Worldwide gross income, duration and actors) affect iMDb ratings and also how many votes were cast for a film to recieve said rating.

#Consider?
Our aim in this project is to find out if there truly is a bias towards films in different languages other then English, if people cant get over the one inch barrier of subtitles. To do this we will mainly use the IMDb ratings to explore this but we will also compare how different variables (title, year published, genre, budget, USA gross income, Worldwide gross income, duration and actors) affect iMDb ratings and also how many votes were cast for a film to recieve said rating.

## 2. Data

```{r read-data}
imdb <- read.csv(file = "../data/IMDb_movies.csv", header = TRUE, skip = 1)
glimpse(imdb)
```

## 3. Data analysis plan

The outcome (response, Y) will be the average imdb ratings, The predictor (explanatory, X) will be country. To properly explore more relationships we will use gross and worlwide income to see if the movie did well worldwide or just in the us. We can also take a look at how factors such as genre, number of votes and duration impact the rating of a movie. We can see how IMDb rates their films in comparison to another rating site, metascore.

```{r data-analysis-country}
imdb_country <- imdb %>%
  mutate(country = case_when(
    country == "Hong Kong" ~ "Hong-Kong",
    country == "South Korea" ~ "South-Korea",
    TRUE ~ country)) %>%
  separate_rows(country)
  
imdb_country %>%
  count(country) %>%
  arrange(desc(n))

imdb_country %>%
  filter(
    country == c("USA", "France", "UK", "India", "Italy", "Germany", "Japan", "Canada", "Spain", "Hong-Kong", "Turkey", "Belgium")
  ) %>%
  group_by(country) %>%
  summarise(
    mean_rating = mean(avg_vote, na.rm = TRUE),
    median_rating = median(avg_vote, na.rm = TRUE)
    ) %>%
  arrange(desc(mean_rating))

imdb_country %>%
  filter(country == c("USA", "France", "UK", "India", "Italy", "Germany", "Japan", "Canada", "Spain", "Hong-Kong", "Turkey", "Belgium")) %>%
  ggplot(aes(x = avg_vote, y = country, fill = country)) +
  geom_density_ridges(alpha = 0.5, show.legend = FALSE) +
  labs(
    title = "Distribution of IMDb Average Ratings",
    subtitle = "for top 12 countries who have produced the most films",
    x = "Average rating",
    y = "Country"
  )
```
After filtering for the top 12 countries who produce the largest number of films, the distribution of `avg_vote` is observed. The countries with the higher ratings include Japan, Belgium, France, Germany and India. Even though the USA has the largest number of films produced, their mean rating is the lowest of these countries.

```{r data-analysis-country-production}
imdb_country %>%
  filter(country != "USA") %>%
  group_by(country) %>%
  summarise(
    mean_rating = mean(avg_vote, na.rm = TRUE),
    count = n()
    ) %>%
  ggplot(aes(x = count, y = mean_rating)) +
  geom_point(alpha = 0.5) +
  geom_smooth() +
  labs(
    title = "Country's Mean Average Rating vs. the Number of Films Produced",
    x = "Count",
    y = "Mean Average Rating"
  )
```

This graph intends to answer the question: Do countries who produce larger amounts of films have an overall higher rating? After grouping by country, the overall average IMDb average rating was calculated along with the amount of movies in each category. This graph reveals that there is little to no association between the amount of films produced and the mean average rating. 

```{r data-analysis-genre}
imdb_genre <- imdb %>%
  mutate(genre = case_when(
    genre == "Sci Fi" ~ "Sci-Fi",
    genre == "Film Noir" ~ "Film-Noir",
    TRUE ~ genre)) %>%
  separate_rows(genre)
  

imdb_genre %>%
  group_by(genre) %>%
  summarise(
    mean_rating = mean(avg_vote, na.rm = TRUE),
    median_rating = median(avg_vote, na.rm = TRUE)
    ) %>%
  arrange(desc(mean_rating))

imdb_genre %>%
  ggplot(aes(x = avg_vote, y = genre, fill = genre)) +
  geom_density_ridges(alpha = 0.5, show.legend = FALSE) +
  labs(
    title = "Distribution of IMDb Average Rating by Genre",
    x = "Average Rating",
    y = "Genre"
  )
```
This graph reveals the distribution of `avg_vote`, which is the rating, for every `genre`. As shown by the graph and the summary statistics, some high rated genres include Documentary, Film Noir, Biography, History, War and News. In these data analyses, films with multiple genres were counted in each of their catagories.

```{r data-analysis-income}
imdb_income <- imdb %>%
  mutate( 
  worlwide_gross_income = na_if(worlwide_gross_income, "")) %>%
  transform(worlwide_gross_income = as.numeric(gsub("\\$", "", worlwide_gross_income)))
   
imdb_income %>%
  ggplot(aes(x = worlwide_gross_income, y = avg_vote)) +
  geom_point(alpha = 0.1) +
  theme(axis.text.x = element_text(angle = 90)) +
  labs(
    title = "Worldwide Gross Income vs. Average Rating",
    x = "Worldwide Gross Income",
    y = "Average Rating"
  )
```
This graph explores the relationship between the `avg_vote` and `worlwide_gross_income`. This graph has a weak positive association suggesting that the more money that is gained from the film, the more likely the film is to be rated well.

```{r data-analysis-votes}
imdb %>%
  ggplot(aes(x = votes, y = avg_vote)) +
  geom_point(alpha = 0.1) +
  labs(
    title = "Average Rating Based on the Popularity of Movie",
    x = "Number of Votes",
    y = "Average Rating"
  )
```
This graph compared `avg_vote` to `votes`, which indicates a movie's popularity. This graph reveals a positive association, suggesting that the more popular a film is the more likely it will be rated higher.

```{r data-analysis-duration}
imdb %>%
  ggplot(aes(x = duration, y = avg_vote)) +
  geom_point(alpha = 0.1) +
  labs(
    title = "Average Rating Based on Duration of a Movie",
    x = "Duration",
    y = "Average Rating"
  )
```
This graph reveals there is little to no association between the `avg_vote` and `duration` of a movie.
