---
title: "Are Subtitles a One-Inch Barrier for American IMDb users?" 
author: <font size='8'>Calcutta Coders <br> Grace South, Fletcher Adams and Mark Corray</font>
institute: <font size='10'>University of Edinburgh</font>
date: <font size = '6'>`r Sys.Date()`</font>
output:
  revealjs::revealjs_presentation:
    self_contained: false
---
---

```{r setup, include=FALSE}
library(rmarkdown)
library(tidyverse)
library(tidymodels)
library(palmerpenguins)
library(knitr)
library(revealjs)
library(broom)
library(ggridges)
library(here)
library(gt)
```

```{r chunk-output, include = FALSE}
knitr::opts_chunk$set(fig.retina = 3, dpi = 300, fig.width = 6, fig.asp = 0.618, out.width = "80%")
```


```{r read-data, include = FALSE}
imdb <- read.csv(file = here("data/IMDb_movies.csv"), header = TRUE, skip = 1, na.strings = c("NA", "", "None"))
imdb1990 <- read.csv(file = here("data/imdb-merge.csv"))
```
## Are US IMDb users biased against foreign movies?
- Investigating how the average rating of US and non-US users is influenced by country of production
- Exploring the influence of other variables including genre and income (US or worldwide) have on this relationship

{data-background-image="img/confetti.jpg"}

## Average Rating

```{r average-rating, echo = FALSE}
imdb %>%
  ggplot(aes(x = avg_vote)) +
  geom_histogram(binwidth = 0.5) +
  labs(
    title = "Distribution of Average Rating",
    x = "Average Rating",
    y = "Frequency"
  ) +
  theme_minimal()
```

## Average Rating by Country

```{r average-rating-country-table, echo = FALSE}
imdb_country <- imdb %>%
  mutate(country = sub("\\ ", "", country)) %>%
  separate_rows(country, sep = "\\,") %>%
  mutate(country = case_when(
    country == "HongKong" ~ "Hong Kong",
    TRUE ~ country)) %>%
  filter(
     country %in% c("USA", "France", "UK", "India", "Italy", "Germany", "Japan", "Canada", "Spain", "Hong Kong", "Turkey", "Belgium")
   )

imdb_country %>%
  group_by(country) %>%
  summarise(
    mean_rating = mean(avg_vote, na.rm = TRUE),
    median_rating = median(avg_vote, na.rm = TRUE)
    ) %>%
  arrange(desc(mean_rating)) %>%
  gt() %>%
  cols_label(
    country = "Country",
    mean_rating = "Mean Rating",
    median_rating = "Median Rating"
  )
```

## Average Rating by Country

```{r average-rating-country, echo = FALSE}
imdb_country %>%
  ggplot(aes(x = avg_vote, y = country, fill = country)) +
  geom_density_ridges(alpha = 0.5, show.legend = FALSE) +
  labs(
    title = "Distribution of IMDb Average Ratings",
    subtitle = "for top 12 countries who have produced the most films",
    x = "Average rating",
    y = NULL
  ) +
  theme_minimal()
```

## Comparison of US vs. non-US users average rating by country 

```{r country-us-rating, echo = FALSE}
imdb1990_country <- imdb1990 %>%
  separate_rows(country, sep = "\\,") %>%
  mutate(country = case_when(
    country == "HongKong" ~ "Hong Kong",
    TRUE ~ country
  )) %>%
  filter(
     country %in% c("USA", "France", "UK", "India", "Italy", "Germany", "Japan", "Canada", "Spain", "Hong Kong", "Turkey", "Belgium")
   ) %>%
  pivot_longer(cols = c(us_rating, non_us_rating), names_to = "us_or_not", values_to = "rating")

imdb1990_country %>%
  ggplot(aes(x = rating, fill = us_or_not)) +
  geom_density(alpha = 0.5) +
  facet_wrap(~ country) +
  labs(
    title = "Average Rating by US or non-US users",
    subtitle = "by country",
    x = "Average Rating",
    y = "Density",
    fill = NULL
  ) +
  theme_minimal()
```
